Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
another update

%% The main goal of our evaluation is to understand what is the impact of
%% \ds{} on \sfl{} after minimizing the $k$ highest faulty source files
%% which comprise the highest faulty statements.

Recall from Section~\ref{sec:approach} that the \comb{}
takes as input a value $k$ that denotes the $k$ most suspicious distinct
classes to be considered. To evaluate the effectiveness of \comb{}, following
related work, we compared its
performance with \sfl{} for each defect on each subject program from
the dataset, for $k\in\{5,10\}$. These classes are obtained directly
from the ranking. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{} using the
following metrics.\Mar{Sofia, I don't see a reason for an equation to
  only show the difference of cost. Please describe precisely the
  metrics. In this case, I can't find what C stands for. Also,
 you need to describe precisely what top@n (or someother name) means
 in this context. Check if it makes sense for SFL.$\rightarrow$}\Rui{It might
 be good to keep it just to give it some emphasis... }

\begin{equation}
    \Delta{}C = C(\textrm{SFL}) - C(\textrm{\combpar{k}})
\end{equation}

\noindent
where $C$ is the cost of diagnosis. \Rui{At this point, you need to explain what
the cost of diagnosis is: C is the number of statemetns (?) that need to be
inspected before finding the fault, right? We also need to say that we assume a
perfect bug understanding: that is, when the developer sees the bug in the
ranking, he can say that it is the faulty one.}
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost to
find the bug.

\subsection{Dynamic Slicing}

This subsection aims to evaluate the performance of the \ds{} technique on slicing
de \dfj{} projects.

@@

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
	\label{tab:red}
\end{table}
\normalsize

Table \ref{tab:red} reports the reduction of statements after using \ds{} to minimize the top-5 and top-10 of classes of the subjects.

@@

\begin{table*}[h]
	\small
	% \setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|cccc|cccc|c}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}         &  55 & 84.6\%  & 55  & 84.6\%
		 				& 65 & 100\% & 63 & 96.9\% & 65      \\
		\cmath{}           & 85 & 81.7\%  & 89 & 85.6\%
						& 93 & 89.4\% & 99 & 95.2\% & 104  \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
	 Total      & 207  & 78.4\% & 217 & 83.0\%
	 				& 227 & 83.8\% & 237 & 88.2\% & 260 \\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Rui{explain what $k$ is for SFL alone.}}
  \label{table:fsws}
\end{table*}

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
		\label{fig:diagnosis}
\end{figure}

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL-5      & SFL-10              & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 584.33  &  516.42  & 679.67 & 613.98   \\ \midrule
Median & 49.38    & 53.00  & 69.25              & 56.93               \\ \midrule
Variance & 1223.08  &  1148.11  & 1352.37  & 1294.87   \\ \midrule
Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

>>>>

To evaluate the effectiveness of \comb{}, following
related work, we compared its
performance with \sfl{} for each fault from
the dataset, for $k\in\{5,10\}$, where $k$ is the number of classes comprising the highest faulty statements. These classes are obtained directly
from the ranking which is calculated through \sfl{}. For each fault, spectra is updated and the fault ranking is re-calculated but only considering the $k$ highest faulty classes. We refer to these variations as SFL$^{k}$. After slicing each class of the top $k$ of the highest faulty classes for each fault, the initial spectra is updated based on the slicer output and the fault ranking is re-calculated. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using the
following metric:

\begin{equation}
    \Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})
\end{equation}

\noindent
where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
locating the bug.

\subsection{Dynamic Slicing}\label{sec:ds}

This subsection aims to report the performance of the \ds{} technique on slicing de faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top $5$ and $10$ of classes comprising the highest faulty statements. Our approach was capable to reduce the \dfj{} projects in an average of 30.23\%.

@@

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance when considering $k=5$ and $k=10$}
	\label{tab:red}
\end{table}
\normalsize

@@

\begin{table*}[h]
	\small
	% \setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|cccc|cccc|c}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{\sfl{}$^{k}$}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}         &  55 & 84.6\%  & 55  & 84.6\%
		 				& 65 & 100\% & 63 & 96.9\% & 65      \\
		\cmath{}           & 85 & 81.7\%  & 89 & 85.6\%
						& 93 & 89.4\% & 99 & 95.2\% & 104  \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
	 Total      & 207  & 78.4\% & 217 & 83.0\%
	 				& 227 & 83.8\% & 237 & 88.2\% & 260 \\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table*}

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$ respectively}
		\label{fig:diagnosis}
\end{figure}

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 584.33  &  516.42  & 679.67 & 613.98   \\ \midrule
Median & 49.38    & 53.00  & 69.25              & 56.93               \\ \midrule
Variance & 1223.08  &  1148.11  & 1352.37  & 1294.87   \\ \midrule
Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}
